Procedural Terrain \\ {\large Final project for class CS6491 Computer Graphics}

### 2015-11-30 Paper/Paper.tex
some improvements of the paper

\section{Vegetation}\label{Vegetation}
Terrain without vegetation looks a little bit boring. Therefore, the last step of the framework is to define biomes and add trees and grass based on it.

@@

The terrain can be rendered using different textures for each biome (Fig. \ref{fig:terrainBiomes}). Furthermore, the biomes specify if and what grass is used and what trees are planted.
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes1}
		\caption{biomes are painted on the terrain}
		\label{fig:terrainBiomes1}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes2}
		\caption{textured terrain based on the biomes}
		\label{fig:terrainBiomes2}
	\end{subfigure}
	\caption{Assigning biomes to the terrain}\label{fig:terrainBiomes}
\end{figure*}

@@

Both problems are adressed with a very simple technique based on impostors for rendering distant trees.
\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.30\textwidth]{images/Impostor}
	\caption{Impostor}
	\label{fig:Impostor}
\end{figure}
impostors are textured quads that are rotated around a central axis. We are using eight quads for trees (Fig. \ref{fig:Impostor}). Note the similarity of the impostors to the way grass is rendered. Each quad is textured with how the tree would look like when seen from the angle of that quad. To create these textures, we render the trees from every of these eight view angles into a offscreen surface and use this as the texture.
During the creation of the textures, the tree must be rendered with exactly the same light setting as in the final scene. Otherwise, the lighting of the tree impostors are not consistent with the lighting of the surrounding terrain. This is especially necessary when a strong directional light is used.

@@

The next two pages show some screenshots from the terrain that is developed through this paper.

>>>>

\section{Vegetation}\label{Vegetation}
Terrain without vegetation looks a little bit boring. Therefore, the last step of the framework is to define biomes and add trees and grass based on them.

@@

The terrain can be rendered using different textures for each biome (Fig. \ref{fig:terrainBiomes}). Furthermore, the biomes specify the existence and types of grass and trees.
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes1}
		\caption{biomes are painted on the terrain}
		\label{fig:terrainBiomes1}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{images/TerrainBiomes2}
		\caption{textured terrain based on the biomes}
		\label{fig:terrainBiomes2}
	\end{subfigure}
	\caption{Assigning biomes to the terrain}\label{fig:terrainBiomes}
\end{figure*}

@@

Both problems are adressed with a very simple technique based on impostors for rendering distant trees.
\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.30\textwidth]{images/Impostor}
	\caption{Impostor}
	\label{fig:Impostor}
\end{figure}
impostors are textured quads that are rotated around a central axis. We are using eight quads for trees (Fig. \ref{fig:Impostor}). Note the similarity of the impostors to the way grass is rendered. Each quad is textured with how the tree would look like when seen from the angle of that quad. To create these textures, we render the trees from every of these eight view angles into a offscreen surface and use this as the texture.
During the creation of the textures, the tree must be rendered with exactly the same light setting as in the final scene. Otherwise, the lighting of the tree impostors is not consistent with the lighting of the surrounding terrain. This is especially necessary when a strong directional light is used.

@@

The next two pages show some screenshots from the terrain used as an example through this paper.
